Analysis of celiac disease

### 2018-03-02 5-results-celiac.Rmd
need to add multiple results

## Predictive models

@@

```{r}
# GWAS
system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
```

@@

>>>>

## Methods' functions

Each method's function returns a tibble (data frame) with 4 columns:

1. the name of the method,
2. the predictive scores and true phenotypes for the test set, as a [list-column](http://r4ds.had.co.nz/many-models.html),
3. the timing of the main computations (in seconds),
4. the number of SNPs used for the prediction.

```{r}
PRS <- function(G, infos.chr, infos.pos, 
                pheno.all, covar.all, 
                ind.train, ind.test) {

  timing <- system.time({

    # GWAS
    gwas.train <- big_univLogReg(
      G, pheno.all[ind.train], ind.train = ind.train, 
      covar.train = covar.all[ind.train, , drop = FALSE], 
      ncores = nb_cores()
    )
    gwas.train.gc <- snp_gc(gwas.train)

    # Clumping on the test set
    ind.keep <- snp_clumping(G, infos.chr = infos.chr,
                             ind.row = ind.test,
                             thr.r2 = 0.2, 
                             S = abs(gwas.train.gc$score),
                             size = 500,
                             is.size.in.bp = TRUE,
                             infos.pos = infos.pos,
                             ncores = nb_cores())

    # PRS
    thrs <- c(0, -log10(5e-8), exp(seq(log(0.1), log(100), length.out = 100)))
    lpS <- -predict(gwas.train.gc)
    nb.pred <- sapply(thrs, function(thr) sum(lpS[ind.keep] > thr))
    prs <- snp_PRS(G, betas.keep = gwas.train.gc$estim[ind.keep],
                   ind.test = ind.test,
                   ind.keep = ind.keep,
                   lpS.keep = lpS[ind.keep], 
                   thr.list = thrs)
  })[3]

  ind.best <- which.max(apply(prs, 2, AUC, target = pheno.all[ind.test]))

  tibble(
    method = "PRS-max",
    eval = list(cbind(prs[, ind.best], pheno.all[ind.test])),
    timing = timing,
    nb.preds = nb.pred[ind.best]
  )
}
```

```{r}
logit.CMSA <- function(G, pheno.all, covar.all, ind.train, ind.test, method, print_all = FALSE) {

  timing <- system.time({

    cmsa.logit <- big_spLogReg(X = G, y01.train = pheno.all[ind.train], 
                               ind.train = ind.train, 
                               covar.train = covar.all[ind.train, , drop = FALSE],
                               ncores = nb_cores())

    preds.all <- predict(cmsa.logit, X = G, ind.row = ind.test, 
                         covar.row = covar.all[ind.test, , drop = FALSE])
    if (print_all) print(preds.all)
    preds <- rowMeans(preds.all)
  })[3]

  tibble(
    method   = method, 
    eval     = list(cbind(preds, pheno.all[ind.test])),
    timing   = timing,
    nb.preds = sum(rowSums(sapply(cmsa.logit, function(x) x$beta.X) != 0) > 0)
  )
}
```

## Predictive models and plots

@@

```{r}
res.PRS <- PRS(
  G = G,
  infos.chr = CHR,
  infos.pos = POS,
  pheno.all = y,
  covar.all = obj.svd$u,
  ind.train = ind.train,
  ind.test = ind.test
)
# GWAS
system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
```

@@

## Predictive methods (multiple times)

```{r}
# Divide in training/test sets
ind.train <- sort(sample(nrow(G), size = 12e3))
ind.test <- setdiff(rows_along(G), ind.train)
```

```{r}
# PRS
PRS <- function() {

  system.time(
  gwas.train <- big_univLogReg(
    G, y[ind.train], ind.train = ind.train, 
    covar.train = obj.svd$u[ind.train, , drop = FALSE], 
    ncores = NCORES
  )
)
}

```
